Quality Definitions of Qualities

### 2019-11-05 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
completed defn reusability

\subsection{Reusability}
\begin{defn} \label{ReusabilityDefnSelected}
The degree to which a software module or other work product can be used in more than one software system \citep{IEEEStdGlossarySET1990}. 
\end{defn}
\begin{defn}
Extent to which a program [or parts of a program] can be reused in other applications - related to the packaging and scope of the functions that the program performs \citep{pressman2005software}.
\end{defn}

\noindent \textbf{Chosen definition:} Definition \ref{ReusabilityDefnSelected} rephrased:

The degree to which a software product can be modularized for easy transferal into other systems.

@@

This definition highlights transferal of parts of the system, or the whole system as a module into another system. Transferal of the whole system onto another environment would be covered in portability.

\pmi{I am still not comfortable with this.}

>>>>

\subsection{Reusability}
\begin{defn} 
The degree to which a software module or other work product can be used in more than one software system \citep{IEEEStdGlossarySET1990}. 
\end{defn}
\begin{defn}
Extent to which a program [or parts of a program] can be reused in other applications - related to the packaging and scope of the functions that the program performs \citep{pressman2005software}.
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected}
The extent to which a software component can be used with or without adaptation in a problem solution other than the one for which it was originally developed \citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
Reusability is the likelihood a segment of source code that can be used again to add new functionalities with slight or no modification \citep{sandhu2010survey}.
\end{defn}

\noindent \textbf{Chosen definition:} Definition \ref{ReusabilityDefnSelected}:

The extent to which a software component can be used with or without adaptation in a problem solution other than the one for which it was originally developed.

@@

This definition highlights the possible but not necessary adaptation of the software component(s) being transferred.
